\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
Stamps Scholarship Selection Committee}

% opening here
\opening{}
\raggedright 
\setlength{\parindent}{15pt}

This letter is in support of MIDN 3/c Sean Kee's application for a Stamps Scholarship. Mr.~Kee was one of my plebe advisees and was a student in my section of EW282C (Introduction to Drone Technology - fixed wing), and has continued on in the Department of Weapons Robotics and Control Engineering. Kee is an excellent student and has outstanding potential for graduate study. 

As a plebe, Mr.~Kee challenged himself academically, taking initiative in his classes and overloading to take my drone class. He has continued in our department as a Robotics and Control Engineering major. Midshipmen in our department must possess the mental gymnastics necessary to balance mechanics, electronics, computer science, and control systems as applied to robotic and autonomous systems. This broad base makes them generally well suited for further graduate study. Kee is naturally inquisitive, strives to learn beyond what is required, and takes full advantage of all available resources; all of which will serve him well in grad school. He has thrived here at USNA even with a high load (21--22 credit hours / semester) and a Chinese language minor.

As a plebe, Mr.~Kee took part in the first offering of EW282C, our School of Drones fixed wing offering.  Kee was responsible for constructing several fixed wing drones (including trainers, flying wing racers, and larger payload platforms) and learning to safely fly them in line of sight, first-person-view, and autonomous modes. As a plebe, Kee was installing and calibrating autopilots and programming autonomous missions; skills some of our firsties never develop. Kee selected an aggressive goal of deploying a swarm of quadcopters from an autonomously flown mothership. While a mishap cut short the first attempt at a demonstration, this has not deterred Kee; with another crop of small quadcopters available this fall we hope to try again. Kee's work ethic in this regard is quite admirable. I hope I am lucky enough to work with him on whatever project he takes on next.

\closing{~} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}

